### 2013-12-28 thesis/src/chapters/chapter-5-design.tex
Thesis: added drawings, resolved conflict

Next section states the general overview of the proposed solution, while the consecutive sections presents more detailed discussion of its elements and finally the last section summarised the design choices in a context of system requirements.

\section{High-level design}
\subsection{Key elements}
In the previous chapters, various scalability models operating at different layers of abstraction were introduced: 
\begin{itemize}
	\item application platform: application platform tuning
	\item container: vertical scaling
	\item stack: horizontal scaling
	\item inter-cloud: scaling out across different cloud providers
\end{itemize}

It is vital that proposed architecture reflects that multi-layered model. Thus, we divided platform's components into a stack that is shown in figure \ref{design:csap-layers}.

@@

\subsection{Autonomic components}
Each layer of the Cloud-SAP (shown in figure \ref{design:csap-layers}) must be characterized by an ability to adapt to a given application usage. As the previous chapter stated, this can be achieved by adding an elasticity controller to each layer. This observation is a foundation of proposed architecture.

@@

Since designed platform operates on multiple layers, we can extend that model by using concept of a multi-hierarchical autonomic system \cite{LiWoZh05}. Figure \ref{design:hierarchical-autonomic-system} illustrates that hierarchy, were each level represents a different perspective on an application scaling. Using terminology characteristic to a autonomic system, first three hierarchy levels (application tuning, container, stack) are centralized and controlled by a single elasticity controller at each level, while the last inter-cloud level is a decentralized one - each cloud instance is fully independent.

@@

\subsection{Architecture overview}
Taking above-mentioned points into account, we can distinguish two pivotal components responsible for auto-scaling and cooperation in intercloud respectively. While each auto-scaling component is entirely dedicated to a given cloud provider, the intercloud module has distributed components such as client and broker and can correspond to a variety of different auto-scaling components. Figure X illustrates overall architecture.

(Diagram komponentowy)

\section{Container controller}

\section{Stack controller}

\section{Cloud controller, cloud broker and client application}

>>>>

Next section states the general overview of the proposed solution, while the consecutive sections presents more detailed discussion of its elements and finally the last section summarises the design choices in a context of system requirements.

\section{High-level design}
\subsection{Overview}

\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=0.8\textwidth]{chapter-5/hld-overview}
  \end{center}
  \caption{Cloud-SAP high level overview}
  \label{design:hld-overview}
\end{figure}

As diagram \ref{design:hld-overview} illustrates, we can distinguish two main components of proposed solution: auto-scaling module and inter-cloud broker. Together, they can be seen as an hierarchical autonomic system, where each layer corresponds to a different scalability perspective:
\begin{itemize}
	\item application platform layer: application platform tuning
	\item container layer: vertical scaling
	\item stack layer: horizontal scaling
	\item inter-cloud layer: scaling out across different cloud providers
\end{itemize}

Diagram \ref{design:csap-layers} depicts that multi-layered structure.

@@

\subsection{Auto-scaling module}

\subsubsection{Autonomic components}
Each layer of the Cloud-SAP (shown in figure \ref{design:csap-layers}) must be characterised by an ability to adapt to a given application usage. As the previous chapter stated, this can be achieved by adding an elasticity controller to each layer. This observation is a foundation of proposed architecture.

@@

Since designed platform operates on multiple layers, we can extend that model by using concept of a multi-hierarchical autonomic system \cite{LiWoZh05}. Figure \ref{design:hierarchical-autonomic-system} illustrates that hierarchy, were each level represents a different perspective on an application scaling. Using terminology characteristic to a autonomic system, first three hierarchy levels (application tuning, container, stack) are centralised and controlled by a single elasticity controller at each level, while the last inter-cloud level is a decentralized one - each cloud instance is fully independent.

\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=0.8\textwidth]{chapter-5/hierarchical-autonomic-system}
  \end{center}
  \caption{Cloud-SAP as an hierarchical autonomic system}
  \label{design:hierarchical-autonomic-system}
\end{figure}

@@

\section{Auto-scaling module}

\section{Cloud federation}

### 2013-12-28 thesis/src/chapters/chapter-7-evaluation.tex
Thesis: added drawings, resolved conflict

\subsection*{Preconditions}
Service specification (\ref{lst:service-spec-test-cost}) forms an input to the application. Its elements are different software stacks that are parts of the whole service. Each cloud provider has its own price for a given software stack which is shown in table \ref{tbl:test-service-deployment-cost}. Diagram \ref{tbl:test-service-deployment-cost-diagram} illustrates the overall configuration.

@@

(JEB deployment diagram, podzial na wezly)

@@

\section{Auto-scaling -- single-provider based}
\subsection*{Description}
\subsection*{Preconditions}
\subsection*{Results}
\subsection*{Conclusion}

\section{Auto-scaling -- multiple-provider based}
\subsection*{Description}
\subsection*{Preconditions}
\subsection*{Results}
\subsection*{Conclusion}

@@

\subsubsection{Hardware configuration}
All virtual machines were deployed on one node which had 3G RAM, AMD Athlon\texttrademark 64 X2 Dual Core Processor with each core of 2000 MHz frequency and a hard drive with a capacity of 160 GB. Diagram presents the physical configuration of nodes.
- jeb physical diagram

@@

\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-7/deployment-time-components}
  \end{center}
  \caption{Deployment diagram of \emph{Carina}}
  \label{ch7:deployment-time-test-deployment-time-components}
\end{figure}

>>>>

\subsection*{Preconditions}
Service specification (\ref{lst:service-spec-test-cost}) forms an input to the application. Its elements are different software stacks that are parts of the whole service. Each cloud provider has its own price for a given software stack which is shown in table \ref{tbl:test-service-deployment-cost}. Diagram \ref{eval:deployment-cost-physical-nodes} illustrates the simplified environment setup.

@@

\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=0.6\textwidth]{chapter-7/deployment-cost-physical-nodes}
  \end{center}
  \caption{Deployment cost: environment configuration}
  \label{eval:deployment-cost-physical-nodes}
\end{figure}

@@

\section{Auto-scaling -- single-provider based}
\subsection*{Description}
\subsection*{Preconditions}
\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=0.8\textwidth]{chapter-7/auto-scaling-1cp-physical-nodes}
  \end{center}
  \caption{Auto-scaling - single-provider based: environment configuration}
  \label{eval:auto-scaling-1cp-physical-nodes}
\end{figure}

\subsection*{Results}
\subsection*{Conclusion}

\section{Auto-scaling -- multiple-provider based}
\subsection*{Description}
\subsection*{Preconditions}
\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=0.8\textwidth]{chapter-7/auto-scaling-2cp-physical-nodes}
  \end{center}
  \caption{Auto-scaling - multiple-provider based: environment configuration}
  \label{eval:auto-scaling-1cp-physical-nodes}
\end{figure}

\subsection*{Results}
\subsection*{Conclusion}

@@

\subsubsection{Hardware configuration}
All virtual machines were deployed on one node which had 3G RAM, AMD Athlon\texttrademark 64 X2 Dual Core Processor with each core of 2000 MHz frequency and a hard drive with a capacity of 160 GB. Diagram presents the physical configuration of nodes.

+ fizycznych

\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=0.6\textwidth]{chapter-7/deployment-time-physical-nodes}
  \end{center}
  \caption{Deployment time - solution comparison: physical environment setup}
  \label{eval:deployment-time-physical-nodes}
\end{figure}

@@

\begin{figure}[!ht]
  \begin{center}
    \includegraphics[width=\textwidth]{chapter-7/deployment-time-components}
  \end{center}
  \caption{Deployment diagram of \emph{Cloud-SAP}}
  \label{ch7:deployment-time-test-deployment-time-components}
\end{figure}
